Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-04 WSSSPE1_report/WSSSPE1_summary_report.tex
Added a TODO note.

>>>>

\todo{Mention somewhere statistics of participants: There were 140 seats, I (Katz) think 149 people at the first keynote, and about 90 at the end of the workshop.  They (SC13) counted people in the room 4 times during the day.  But I don’t know how many unique people attended, which I agree they should know.}
